\chapter*{Abstract}
The objective of this Doctoral Thesis was to develop, implement and test new algorithms for the large-scale solution of nonstationary compressible MHD equations based on higher-order discontinuous Galerkin (DG) methods. The basis for the new methods will be the discontinuous Galerkin methods and adaptive mesh refinement (AMR) algorithms. The new algorithms will be implemented and tested in the framework of the open source library deal.II, and they will be applied to selected existing benchmarks for magnetohydrodynamic phenomena and real problems of MHD in astrophysics.

\section*{Keywords}
numerical simulation, finite element method, MHD equations, adaptivity, discontinuous Galerkin method, astrophysics, solar flares, AMR, distributed computing

\chapter*{Abstract [CZ]}
Zámìrem této práce je navrhnout, implementovat a otestovat nové algoritmy pro rozsáhlé simulace nestacionárních jevù spadajících do oblasti stlaèitelné magnetohydrodynamiky. Vytvoøený software bude založen na použití nespojité Galerkinovy metody (discontinuous Galerkin, DG) s vyššími øády pøesnosti. Zároveò bude použita metoda automatického zjemòování výpoèetní triangulace (automatic mesh refinement, AMR). Vytvoøené algoritmy budou testovány ve frameworku deal.II a budou aplikovány na existující benchmarky pro magnetohydrodynamické jevy a na skuteèné problémy v astrofyzice.

\section*{Keywords [CZ]}
numerická simulace, metoda koneèných prvkù, MHD rovnice, adaptivní algoritmy, nespojitá Galerkinova metoda, astrofyzika, sluneèní erupce, AMR, distribuované výpoèty


\chapter*{Acknowledgement}
I hereby acknowledge and thank for the lead and support of my supervisor, prof. Ing. Pavel Karban, Ph.D., as well as my advisor prof. Ing. Ivo Doležel, CSc. I would also like to thank Mgr. Miroslav Bárta, Ph.D. from the Department of Solar Physics of the Astronomical Institute of the Czech Academy of Sciences to give me valuable insight into the problems of astrophysics, and I also hereby appreciate the work of the entire deal.II development team for their professional approach to software development and support.

\chapter*{Statement}
I am presenting this doctoral thesis, created during my doctoral studies at the Faculty of Electrical Engineering of the University of West Bohemia.
\\
\vspace{3em}
\\
I confirm having prepared this work by my own, and having listed all used sources of information in the bibliography. All license conditions of all works of software and other nature were respected.
\\
\vspace{6em}
\\
In Pilsen, \today, Lukáš Korous