\chapter*{Abstract}
The objective of this Doctoral Thesis was to develop, implement and test new algorithms for the large-scale solution of nonstationary compressible MHD equations based on higher-order discontinuous Galerkin (DG) methods. The basis for the new methods will be the discontinuous Galerkin methods and adaptive mesh refinement (AMR) algorithms. The new algorithms will be implemented and tested in the framework of the open source library Deal.II, and they will be applied to selected problems of MHD in astrophysics, namely the magnetic reconnection phenomena.

\section*{Keywords}
numerical simulation, finite element method, MHD equations, adaptivity, discontinuous Galerkin method, astrophysics, solar flares, CME, magnetic reconnection

\chapter*{Abstract [CZ]}
TODO

\section*{Keywords [CZ]}
TODO


\chapter*{Acknowledgement}
TODO - prelozit

Za skvělé vedení při studiu a práci, časté konzultace a odbornou pomoc zaslouží obrovské díky především prof. Ing. Ivo Doležel, CSc. a doc. Ing. Pavel Karban, Ph.D., kteří se stali mými dlouholetými kolegy a přáteli. Dále bych rád poděkoval všem kolegům se kterými jsem měl tu čest spolupracovat. V~neposlední řadě bych také rád poděkoval své rodině za její neuvěřitelnou výdrž a podporu.

\chapter*{Statement}
TODO - prelozit

Předkládám tímto k~posouzení tezi dizertační práce, zpracovanou na během doktorského studia na Fakultě elektrotechnické Západočeské univerzity v~Plzni.
\\
\vspace{1em}
\\
Prohlašuji, že jsem tuto práci vypracoval samostatně, s~použitím uvedené odborné literatury, a pramenů a že veškerý software, použitý při jejím řešení a zpracování, byl využit s~respektováním všech jeho licenčních podmínek.
\\
\vspace{3em}
\\
In Pilsen, \today, Lukáš Korous